\documentclass[11pt, oneside]{report}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bbold}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{slashed}

%\newcommand{\cref}[1]{Eq.(\ref{#1})}
\newcommand{\ie}{\textit{i.e., }}
\newcommand{\eg}{\textit{e.g. }}
\newcommand{\wrt}{w.r.t. }
\newcommand{\rhs}{r.h.s. }
\newcommand{\lhs}{l.h.s. }
\newcommand{\eval}[1]{\bigg\rvert_{#1}}
\newcommand{\dd}{\textrm{d}}
%\newcommand{\de}{\textrm{e}}
\newcommand{\im}{\mathrm{Im}}
\newcommand{\ran}{\mathrm{Ran}}
\newcommand{\rank}{\mathrm{Rank}}
\newcommand{\dom}{\mathrm{Dom}}
\newcommand{\en}{\mathrm{End}}
\newcommand{\tr}{\mathrm{Tr}}
\newcommand{\grad}{\mathrm{grad}}

%equation with split DOESN'T WORK...
%\def\sequation#1#2{\begin{equation}\label{#2}\begin{split}{#1} \end{split} \end{equation} }
%\def\sequationstr#1{\begin{equation*}\begin{split}{#1} \end{split} \end{equation*}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{}
\author{}
%\date{}							% Activate to display a given date or no date
\begin{document}
%\maketitle

%\include{data/chap-vacuum/chap-vacuum}
%\include{data/chap-wentzell/chap-wentzell}
\include{data/chap-ym/chap-ym}

\begin{thebibliography}{9}
%Zahn
\bibitem{Zahn2015} J. Schlemmer, J. Zahn, \textit{The current density in quantum electrodynamics in external potentials}, arXiv:1501.05912v2[hep-th], 2015
\bibitem{Zahn2016} J. Zahn, \textit{Generalized Wentzell boundary conditions and holography}, arXiv:1512.05512v2[math-ph], 2016
%mathematics
\bibitem{Reed1981} M. Reed, B. Simon, \textit{Methods of modern mathematical physics I: functional analysis}, revised and enlarged edition (Academic Press, 1981)
\bibitem{Reed1975} M. Reed, B. Simon, \textit{Methods of modern mathematical physics II: Fourier analysis, self-adjointness} (Academic Press, 1975)
\bibitem{Snygg1997} J. Snygg, \textit{Clifford Algebra - A Computational Tool for Physicists} (Oxford University Press, 1997)
\bibitem{Polchinski1998} J. Polchinski, \textit{String Theory - Volume II: Superstring Theory and Beyond} (Cambridge University Press 1998)
\bibitem{Taylor1997} M. E. Taylor, \textit{Partial Differential Equations I} (Springer-Verlag New York, corrected edition 1997)
\bibitem{Gustafson2003} S. J Gustafson, I. M. Sigal, \textit{Mathematical Concepts of Quantum Mechanics} (Springer-Verlag Berlin Heildelberg 2003)
\bibitem{Zeidler1995} E. Zeidler, \textit{Applied Functional Analysis - Applications to Mathematical Physics} (Springer-Verlag New York, 1995)
\bibitem{Hebey1996} E. Hebey, \textit{Sobolev Spaces on Riemann Manifolds} (Springer-Verlag Berlin Heidelberg 1996)
\bibitem{Lang1999} S. Lang \textit{Fundamental of differential geometry} (Springer-Verlag New-York 1999)
\bibitem{Eichhorn1996} J. Eichhorn, J. Fricke of Greifswald, \textit{The Module Structure Theorem for Sobolev Spaces on Open Manifolds}, Math. Nachr. 194 (1998), 35-47 
\bibitem{Trautman2007} A. Trautman, \textit{Connections and the Dirac operator on spinor bundles}, Journal of Geometry and Physics 58 (2008) 238-252
\bibitem{Lawson1989} H. B. Lawson JR., M.-L. Michelsohn, \textit{Spin Geometry} (Princeton University Press 1989)
\bibitem{Alagia1985} H.R. Alagia, C.U. Sánchez, \textit{Spin structures on pseudo-Riemannian manifolds}, Revista de la Unión Matemática Argentina, Vol. 32, 1985
\bibitem{Milnor1974} J.W. Milnor, J.D. Stasheff, \textit{Characteristic Classes} (Princeton University Press 1974)
%\bibitem{Ahluwalia1991} D. V. Ahluwalia, PhD Thesis of Texas A&M University (1991)
%wentzell
\bibitem{Chodos1974} A. Chodos et al., A New Extended Model of Hadrons, Phys. Rev. D9 (1974) 3471.
\bibitem{Contino2005} R. Contino, A. Pomarol, \textit{Holography for fermions}, JHEP 0411, 058 (2004) [arXiv:hep-th/0406257]
\bibitem{Henningson1998} M. Henningson and K. Sfetsos, \textit{Spinors and the AdS/CFT correspondence}, Phys. Lett. B 431, 63 (1998) [arXiv:hep-th/9803251]
\bibitem{Pal2015} P. B. Pal, \textit{Representation-independent manipulations with Dirac matrices and spinors}, arXiv:physics/0703214v4 [physics.ed-ph]
%vacuum polarisation
\bibitem{Milton2001} K. A. Milton, \textit{The Casimir effect - Physical Manifestation of Zero-Point Energy} (World Scientific 2001)
\bibitem{Schwinger1951} J. S. Schwinger, \textit{On gauge invariance and vacuum polarization}, Phys. Rev. 82 (1951) 664
\bibitem{Grib1994} A. A. Grib, S. G. Mamayev, V. M. Mostepanenko, \textit{Vacuum Quantum Effects in Strong Fields} (St. Petersburg, Friedmann Laboratory Publishing, 1994)
%YM
\bibitem{Yang1954} C. N. Yang, R. L. Mills, \textit{Conservation of isotopic spin and isotopic gauge invariance}, Phys. Rev. 96, 191 (1954)
\bibitem{Tao2003} T. Tao, \textit{Local well-posedness of the Yang-Mills equation in the temporal gauge below the energy norm}, Journal of Differential Equations, Vol. 189, Issue 2 (2003), 366-382
\bibitem{Sinatycki1993} J. Sniatycki, G. Schwarz, \textit{The existence and uniqueness of solutions of Yang-Mills equations with bag boundary conditions}, Commun. Math. Phys. 159, 593-604 (1994)
\bibitem{Ginibre1981} J. Ginibre, G. Velo, \textit{The Cauchy Problem for Coupled Yang-Mills and Scalar Fields in the Temporal Gauge}, Commun. Math. Phys. 82, 1-28 (1981)
\bibitem{Arnowitt1962} R. L. Arnowitt, S. I. Fickler, \textit{Quantization of the Yang-Mills Field}, Phys. Rev. 127, 1821 (1962)
%Hodge
\bibitem{Ivancevic2011} V. G. Ivancevic, T. T. Ivancevic, \textit{Undergraduate lecture notes in De Rham-Hodge Theory}, arXiv:0807.4991v4 [math.DG] (2011)
\bibitem{Goldshtein2006} V. Gol'dshtein, M. Troyanov, \textit{Sobolev inequalities for differential forms and $L_{p,q}$-Cohomology}, The journal of geometric analysis, Vol. 16, No. 4 (2006)
\bibitem{Frankel1997} T. Frankel, \textit{The geometry of physics} (Cambridge 1997)
%Sobolev on p-forms
\bibitem{Mazya2009} V. Maz'ya, \textit{Sobolev Space in Mathematics II} (Springer New York 2009) 
\end{thebibliography}
%perhaps useful for causal propagation ???
%C. J. Fewster and B. Mistry \textit{Quantum weak energy inequalities for the Dirac field in flat spacetime}
%Phys. Rev. D 68, 105010 (2003) 

%Distribution Theory for Discontinuous Test Functions and Differential Operators with Generalized Coefficients
%P. Kurasov*



\end{document}









