\section{Introduction}
Quantum field theories in external potential have gained importance these years due to the progress in experimental technology on intensive lasers and measurement of higher precision.
Especially, the quantum electrodynamics in such circumstance becomes a great interest~\cite{Mohr1998}. 
%add more blabla stuffs?
%Quantum electrodynamics has been well tested in weak external fields.
Its present form is basically due to Schwinger. 
In his paper~\cite{Schwinger1951}, the point-splitting formalism is used. 
However, it seems that his approach in~\cite{Schwinger1951} leads to some results which are not gauge invariant. 
\cite{Zahn2015} highlights this point and proposes another approach using Dirac's method~\cite{Dirac1934} and some notions developped in \textit{quantum field theory in curved space-time} (QFT in curved space-time). 
Dirac's method consists of considering the vacuum as a space occupied by negative-energy positrons and that nearly all the positive-energy states are unoccupied.
In presence of an external potential, positrons will occupy some positive-energy states, which leads to the polarization of the vacuum.
A precise definition of the vacuum polarization will be given in this section.
In this report, we compute the vacuum polarization of a spatially confined $(1+1)$-dimensional space in presence of a punctual potential commonly used to explain the Kondo effect. 
By simplicity, we will only consider the vacuum polarization due to massless spin-$\frac 1 2$ particles.
The results can be extended to massive field with the same calculation.
\\\\
%
%
%
\paragraph{QFT in curved space-time}
QFT in curved space-time is a semi-classical theory aiming to take into account the curvature of space-time in quantum field theory.
A review on the necessary notions for this report will be given in this paragraph.
For a more complete review of this subject, we can refer to~\cite{Hollands2014}. \\\\
%
For a given curved Lorentzian space-time $(M,g)$,
the construction of the theory is based on algebraic approach.
Instead of considering a given Hilbert space, 
the theory is formulated with an algebra of quantum observables $\mathscr{A}(M,g)$.
As done in the section 2 of~\cite{Hollands2014}, we give here a brief review of QFT in curved space-time for quantum algebra of observables generated by a Klein-Gordon field $\phi$. 
However, the field $\phi$ should be treated as general function, \ie  distribution.
As a quantized field, the contribution of high frequency modes makes it difficult to define $\phi$ at a precise point $x$.
Hence, $\phi$ should be smeared with some test function $f\in C^\infty_0(M)$ when we want to study related relations.
The smearing $\phi(f)$ is given by
\begin{equation*}
\phi(f) = \int_M \phi f
\end{equation*}
We can then construct $\mathscr{A}(M,g)$ by starting with the free *-algebra generated by unit element $\mathbf{1}$ and elements $\phi(f)$ with $f\in C^\infty_0(M)$ and imposing the following relations \\
\begin{enumerate}
\item \textbf{Linearity} $\phi(c_1 f_1 + c_2 f_2) = c_1 \phi(f_1) + c_2 \phi(f_2)$ for $c_1, c_2 \in \mathbb{C}$
%
\item \textbf{Klein-Gordon equation} $\phi\big( (\Box_g - m^2)f \big) = 0$
%
\item \textbf{Hermitian field} $\phi(f)^* = \phi(\bar{f})$
%
\item \textbf{Canonical commutation relation (CCR)} $[\phi(f_1), \phi(f_2)] = iE(f_1, f_2) \mathbf{1}$, where $E = E^+ - E^-$ and $E^\pm$ are distributions satisfying $(\Box_g - m^2)E^\pm(x,y) = \delta(x,y)$ with appropriate supports (which define the advanced and retarded operators).
\end{enumerate}
%
We define a \textbf{physical state} $\omega$ as a linear map
$\omega: \mathscr{A}(M,g) \rightarrow \mathbb{C}$ satisfying the normalization condition $\omega(\mathbf{1}) = 1$ and the positivity $\omega(a^*a) \geq 0$ for $a\in\mathscr{A}(M,g)$.
A physical state could simply be considered as an expectation value functional. 
For a given state $\omega$, there is an associated Hilbert space $\mathscr{H}_\omega$, a representation $\pi : \mathscr{A}(M,g)\rightarrow \mathscr{H}_\omega$ and a non-trivial vector $\Psi \in \mathscr{H}_\omega$ such that for $a \in \mathscr{A}(M,g)$
\begin{equation*}
\omega(a) = \frac{\langle \Psi, \pi(a)\Psi\rangle}{\langle \Psi, \Psi \rangle}
\end{equation*}
by the GNS-construction (see \eg the appendix of~\cite{Timmermann2008} for more detail).
For what concerns this projet, the physical state that we will be interested in is the vacuum $(d+1)$-current in a $(d+1)$-dimensional space-time.
The definition of such a current will be given later. \\\\
%
Especially, it is of big interest to study physical states which are \textbf{2-point functions} (or more precisely, 2-point distributions), 
\ie distribution $W$ defined by (smeared) 
\begin{equation*}
W_2(f, g ) \equiv \omega(\phi(f)\otimes \phi(g))
\end{equation*}
It should be noted that $W_2(x,y)$ is defined only in sense of distribution because of the divergence when the coinciding-point limit $x\rightarrow y$ is applied.
In a globally hyperbolic space-time $(M,g)$ (see~\cite{Wald2010} for definition), it is shown (theorem 5.1 of~\cite{Radzikowski1996}) that the singular behaviour of the two-point function takes the same form for the states verifying a certain relation (such states are called \textbf{Hadamard states}). 
It is proven in~\cite{Fulling1978} that the singular structure of a Hadamard state is preserved in a globally hyperbolic space-time. 
The singular part at the coinciding-point limit of a Hadamard state is called \textbf{Hadamard parametrix}.
The subtraction of the Hadamard parametrix is a method to renormalize the expectation functional $\omega$. \\\\
%more explaination ??
%
However, as we are interested in QED in this report, the above-mentioned theory is not applicable. 
In particular, the fermionic nature of electron should not be supposed to obey the commutation relation but rather the \textbf{canonical anti-commutation relation} (CAR).
With the same notation as for the commutation relation, 
for a Dirac field $\psi$, the anti-commutation relation is defined by
\begin{equation*}
\{\psi(f_1), \psi(f_2)\} = i S(f_1, f_2) \mathbf{1}
\end{equation*}
where $\{\cdot, \cdot\}$ is the anti-commutator and $S$ is the difference between the advanced and retarded propagators of the Dirac operator (with mass m) $i\slashed{\nabla} - m$.
Also, the fields are supposed to verify Dirac equation instead of just Klein-Gordon equation.
After different works, the characterization developed in~\cite{Radzikowski1996} is generalized in~\cite{Sahlmann2000} to the Dirac field case.
Without introducing the mathematically rigorous definition\footnote{
To give a mathematically rigorous statement of this relation, 
the notion of \textbf{wave front set} is needed. 
We refer to~\cite{Radzikowski1996} for more details.
}, 
we write down the characterization of a 2-point Hadamard state $\omega$ as in~\cite{Zahn2015}
\begin{equation}\label{vacuum-hadamardcond}
\begin{split}
\omega(\psi^B(x)\bar{\psi}_A(x')) + \omega(\bar{\psi}_A(x')\psi^B(x)) = &
iS^B_A(x,x') \\
\overline{\omega(\bar{\psi}(u)\psi(\bar{v}))} = & \omega(\bar{\psi}(v)\psi(\bar{u}))
\end{split}
\end{equation}
where $A$ and $B$ are component indices for the co-spinor $\bar{\psi}$ and the spinor $\psi$ and $\omega$ should take positive (respectively, negative) frequency in the first (respectively, second) argument.
To be more precise, 
by frequency we mean the co-vector corresponding to the time component of the coordinate in the Fourier space.
One can associate this quantity to the "energy" of a given mode. 
We should note that the tensorial product of two Dirac fields is implicitly understood in the argument of $\omega$. 
In addition, we should recall the distributional nature of the Dirac field that we use here. 
Hence, the first equation of~\cref{vacuum-hadamardcond} should be understood in the sense of distribution,
while the second one is smeared with some test sections $u$ and $\bar{v}$. \\\\
Now, let us define the vacuum current with Dirac's method~\cite{Dirac1934}.
If we suppose that positrons should only occupy negative-energy states in a non-polarized vacuum, 
the vacuum polarization could be considered as the occupation of positive-energy states by positrons. 
Since the field of positron satisfies Dirac's equation, 
we define the vacuum $d+1$-current density (in $d+1$-dimensional space-time) as the sum of the current densities of all possible modes which are of positive energy. 
Naively, we would like to define the vacuum current density by the coinciding-point limit of the two-point function
\begin{equation}\label{vacuum-2pointfct}
j'^{\mu}(x,y) =  e \int_{E_k > 0} \bar{\psi}_k(y)\gamma^\mu \psi_k(x) e^{- i E_k(x^0 - y^0)} \dd k
\end{equation}
where $\psi_k$ is the coefficient corresponding to the $k$-mode in the mode expansion and $\gamma^\mu$ are the Dirac gamma matrices.
The convergence of this expression is not ensured because of the infinite number of modes (UV-divergence).
Meanwhile, we recognize a Hadamard state from~\cref{vacuum-2pointfct} defined by 
\begin{equation*}
\begin{split}
\omega(\psi^B(x)\bar{\psi}_A(y)) = & \int_{E_k >0} \psi_k^B(x)\bar{\psi}_{A,k}(y)e^{-i(x^0-y^0)E_k} \dd k \\
\omega(\bar{\psi}_A(y)\psi^B(x)) = & \int_{E_k <0} \psi_k^B(x)\bar{\psi}_{A,k}(y)e^{-i(x^0-y^0)E_k} \dd k 
\end{split}
\end{equation*}
such that 
\begin{equation*}
j'(x,y) = \gamma^A_B \omega(\psi^B(x)\bar{\psi}_A(y)) 
\end{equation*}
where the summation over the repeated indices is used.
Therefore, if the Hadamard paramtrix $H$ is known, we can get a renormalized vacuum current
\begin{equation}\label{vacuum-currentexpression}
j^\mu(x) = \lim_{y \rightarrow x} \gamma^A_B \big(
\omega(\psi^B(x)\bar{\psi}_A(y)) - H^B_A (x, y)\big)
\end{equation}
%
\paragraph{Computation of the Hadamard parametrix}
In this report, the Hadamard parametrix used for our calculation is obtained in~\cite{Zahn2015}. 
Here, we will just give the main idea of the computation of Hadamard parametrices. 
For more detailed mathematical aspects, one can refer to~\cite{Bar2008}
As we will discuss about Dirac fields which are in the kernel of the operator $i\slashed{\nabla} - m$ (eventually $m=0$ for massless cases), 
we have to calculate the retarded and the advanced propagators of 
\begin{equation*}
P = (i\slashed{\nabla} - m)(-i\slashed{\nabla} -m) 
\end{equation*}
It is a normally hyperbolic differential operator (\cite{Bar2008} for definition).
The retarded and advanced propagators are the distributional solutions $\Delta$ of
\begin{equation*} 
P\Delta = \delta_x
\end{equation*}
with appropriate supports.
Such solutions are given by 
\begin{equation*}
\Delta(x,x') = \sum_{k=0}^\infty V_k(x,x') R_{2k+2}(x,x')
\end{equation*} 
where $V_k$ are \textit{Hadamard coefficients} satisfying certain recursive relation and $R_{2k+2}$ are so-called \textit{Riesz distributions}.
The distributional nature of the Riesz distributions gives raise to singularities when coinciding-point limit is applied. 
We can thus build a Hadamard parametrix for the operator $P$.
However, the differential operator of the problem is the Dirac operator $i\slashed{\nabla} -m$,
the corresponding propagators still remains to be found. \\\\
%
As $\Delta$ is now in the kernel of $P$ in the sense of distribution, 
%$\Delta^{\textrm{ret/adv}}\equiv \Delta^{\textrm{ret}} - \Delta^{\textrm{adv}}$,
we can defined the retarded and advanced propagators as 
\begin{equation*}
S^{\textrm{ret/adv}} = (-i\slashed{\nabla} - m)\Delta^{\textrm{ret/adv}} 
\end{equation*}
with appropriate supports.
One can verify easily that $S$ is in the kernel of the Dirac operator $i\slashed{\nabla} - m$.
We build the Hadamard parametrix $H$ of the Dirac operator by choosing distributions that allow us to get the same singularities at coinciding-point limit as in Riesz distributions such that $H$ satisfied
\begin{equation*}
H^+(x,x') - H^-(x,x') = i\big(S^{\mathrm{ret}}(x,x') - S^{\mathrm{adv}}(x,x')\big)
\end{equation*}
%add something to microlocal stuffs
By consequence, for any state $\omega$ with Hadamard two-point function, the following relations hold
\begin{equation*}
\begin{split}
\omega(\psi^B(x)\bar{\psi}_A(y)) = & H^+(x,y)^B_A + R^B_A(x,y) \\
\omega(\bar{\psi}_A(y)\psi^B(x)) = &- H^-(x,y)^B_A - R^B_A(x,y)
\end{split}
\end{equation*}
where $R$ is smooth and determined up to terms vanishing at coinciding-point limit.
%
%
%
%Kondo
\paragraph{Kondo effect}
We propose to evaluate the vacuum polarization of a system (confined or not) 
%check...
in presence of a Kondo type potential.
This type of potential has been proposed by Jun Kondo in~\cite{Kondo1964} in order to study the so-called \textit{Kondo effect}.
Since the 1930's, people have observed anomalies in electrical resistance for some materials when the temperature decreases. 
Rather than having a decreasing resistance when the temperature gets down,
the resistance of certain types of material increases. 
A satisfactory explanation is that this phenomenon would be due to the existence of magnetic impurities in the material. 
Kondo's paper~\cite{Kondo1964} treats this phenomenon as an interaction between spins of conduction electrons and impurities.
As the impurities are considered as punctual,
the Hamiltonian of the Kondo effect in real space (rather than Fourier mode space) is given by~\cite{Erdmenger2013}
\begin{equation}\label{vacuum-kondohamiltonian}
H_K = \psi_\alpha^\dagger \frac{-\nabla^2}{2m}\psi_\alpha +
\frac 1 2\lambda_K \delta(\vec{x})\vec{S}\cdot \psi_{\alpha'}^\dagger  \vec{\sigma}_{\alpha' \alpha} \psi_\alpha
\end{equation}
where $\psi$ and $\psi^\dagger$ are annihilation and creation operator, 
$\alpha$ is the indice for spin (up or down), 
$\vec{S}$ is the spin of the impurity,
$\delta$ is the Dirac distribution,
$\vec{\sigma}$ represents the vector of Pauli matrices and $\lambda_K$ is the Kondo coupling constant (positive for anti-ferromagnetic and negative for ferromagnetic).
















